Comparison of Fast Imaging Architectures for Large, Multi-scale, Hierarchical Aperture Arrays

### 2024-06-05 ms.tex
Update on Overleaf.

A simultaneous beamforming filling the entire field of view can also be achieved by a two-dimensional spatial Fast Fourier Transform (FFT) of the measurements on the aperture plane. This can be enabled even for an irregular layout of station elements by gridding the calibrated electric fields measured by the station elements. The Optimal Map Making formalism \citep[OMM;][]{Tegmark+1997a} formalism adopted by \citet{Morales2011} is the basis of the architecture called E-field Parallel Imaging Correlator \cite[EPIC;][]{Thyagarajan+2017},
\begin{align}
    \widetilde{\mathcal{E}}_m^\alpha(\hat{\boldsymbol{s}}_k) &= \sum_j \delta^2 \boldsymbol{r}_j \, e^{i\frac{2\pi}{\lambda} \hat{\boldsymbol{s}}_k\cdot\boldsymbol{r}_j} \left(\sum_{a_m} \sum_p \widetilde{W}_{a_m}^{p\alpha*}(\boldsymbol{r}_j-\boldsymbol{r}_{a_m}) \, \widetilde{E}_{a_m}^p \right) \, , \label{eqn:intra-station-pol-hol-img-epic}
\end{align}
whose equivalent linear algebraic representation is 
\begin{align}
    \widetilde{\boldsymbol{\mathcal{E}}}_{[m,\alpha,\hat{\boldsymbol{s}}]} &= \mathbf{F}^\textrm{H}_{[\hat{\boldsymbol{s}}\leftarrow \boldsymbol{r}]}\,\widetilde{\mathbf{W}}^\textrm{H}_{[\alpha,\boldsymbol{r}\leftarrow p,\boldsymbol{r}_{a_m}]}\,\widetilde{\mathbf{E}}_{[p,\boldsymbol{r}_{a_m}]} \, . \label{eqn:intra-station-pol-hol-img-epic-LA}
\end{align}

@@

\begin{figure*}\ContinuedFloat
\subfloat[][\texttt{CASPA} \label{fig:1D-coherent-compcost-CASPA}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_CASPA.pdf}
} \\
\subfloat[][\texttt{FarView} \label{fig:1D-coherent-compcost-FarView}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_FarView.pdf}
}
\caption{Contd. Same as above but for (d) \texttt{CASPA}, and (e) \texttt{FarView} \label{fig:1D-incoherent-compcost}}
\end{figure*}

@@

\begin{tabular}{ccccc}

@@

\headrow Architecture & Components & Intra-station & Inter-station & Equations \\
 & (Timescale) & FLOP count & FLOP count & \\ 
 & & (per station & (per voxel) & \\
 & & per voxel) & & \\

@@

VBF & Beamforming ($\delta t$) & $8 n_\textrm{p}^2 N_\textrm{a/s}$ & $8 n_\textrm{p}^2 N_\textrm{s}$ & \ref{eqn:intra-station-pol-hol-img-expl}, \ref{eqn:inter-station-pol-hol-img-expl} \\
& Squaring ($\delta t$) & $6 n_\textrm{p}^2$ & $6 n_\textrm{p}^2$ & \ref{eqn:intra-station-opt-pol-img-outprod} , \ref{eqn:inter-station-opt-pol-img-outprod}  \\
& Accumulation ($\delta t$) & $2 n_\textrm{p}^2$ & $2 n_\textrm{p}^2$ & \ref{eqn:intra-station-opt-pol-img-outprod}, \ref{eqn:inter-station-opt-pol-img-outprod} \\

@@

EPIC & Gridding ($\delta t$) & $\frac{6 n_\textrm{p}^2 N_\textrm{a/s} N_\textrm{ka}}{(D_\textrm{s}/D_\textrm{a})^2}$ & $\frac{6 n_\textrm{p}^2 N_\textrm{s} N_\textrm{ks}}{(D_\textrm{A}/D_\textrm{s})^2}$ & \ref{eqn:intra-station-pol-hol-img-epic-LA}, \ref{eqn:inter-station-pol-hol-img-epic-LA}   \\
& FFT ($\delta t$) & $8 n_\textrm{p} \frac{r}{\log_2 r} \gamma_\textrm{s}^2 \log_2\left(\gamma_\textrm{s}\frac{D_\textrm{s}}{D_\textrm{a}}\right)^2$ & $8 n_\textrm{p} \frac{r}{\log_2 r} \gamma_\textrm{A}^2 \log_2\left(\gamma_\textrm{A}\frac{D_\textrm{A}}{D_\textrm{S}}\right)^2$ & \ref{eqn:intra-station-pol-hol-img-epic-LA}, \ref{eqn:inter-station-pol-hol-img-epic-LA} \\
& Squaring ($\delta t$) & $6 n_\textrm{p}^2 \gamma_\textrm{s}^2$ & $6 n_\textrm{p}^2 \gamma_\textrm{A}^2$ & \ref{eqn:intra-station-opt-polarimetric-direct-img-LA}, \ref{eqn:inter-station-opt-polarimetric-direct-img-LA} \\
& Accumulation ($\delta t$) & $2 n_\textrm{p}^2 \gamma_\textrm{s}^2$ & $2 n_\textrm{p}^2 \gamma_\textrm{A}^2$ & \ref{eqn:intra-station-opt-polarimetric-direct-img-LA}, \ref{eqn:inter-station-opt-polarimetric-direct-img-LA} \\

@@

XBF & Correlator ($\delta t$) & $\frac{6 n_\textrm{p}^2 N_\textrm{a/s} (N_\textrm{a/s}-1)/2}{(D_\textrm{s}/D_\textrm{a})^2}$ & $\frac{6 n_\textrm{p}^2 N_\textrm{s} (N_\textrm{s}-1)/2}{(D_\textrm{A}/D_\textrm{s})^2}$ & \ref{eqn:intra-station-pol-visibilities}, \ref{eqn:inter-station-pol-visibilities}  \\
& Accumulation ($\delta t$) & $\frac{2 n_\textrm{p}^2 N_\textrm{a/s} (N_\textrm{a/s}-1)/2}{(D_\textrm{s}/D_\textrm{a})^2}$ & $\frac{2 n_\textrm{p}^2  N_\textrm{s} (N_\textrm{s}-1)/2}{(D_\textrm{A}/D_\textrm{s})^2}$ & \ref{eqn:intra-station-pol-visibilities}, \ref{eqn:inter-station-pol-visibilities}  \\
& DFT ($t_\textrm{acc}$) & $8 n_\textrm{p}^2 N_\textrm{a/s} (N_\textrm{a/s}-1)/2$ & $8 n_\textrm{p}^2 N_\textrm{s} (N_\textrm{s}-1)/2$ & \ref{eqn:intra-station-pol-xbf-img-expl}, \ref{eqn:inter-station-pol-xbf-img-expl}  \\

@@

XFFT & Correlator ($\delta t$) & $\frac{6 n_\textrm{p}^2 N_\textrm{a/s} (N_\textrm{a/s}-1)/2}{(D_\textrm{s}/D_\textrm{a})^2}$ & $\frac{6 n_\textrm{p}^2 N_\textrm{s} (N_\textrm{s}-1)/2}{(D_\textrm{A}/D_\textrm{s})^2}$ & \ref{eqn:intra-station-pol-visibilities}, \ref{eqn:inter-station-pol-visibilities}  \\
& Accumulation ($\delta t$) & $\frac{2 n_\textrm{p}^2 N_\textrm{a/s} (N_\textrm{a/s}-1)/2}{(D_\textrm{s}/D_\textrm{a})^2}$ & $\frac{2 n_\textrm{p}^2 N_\textrm{s} (N_\textrm{s}-1)/2}{(D_\textrm{A}/D_\textrm{s})^2}$ & \ref{eqn:intra-station-pol-visibilities}, \ref{eqn:inter-station-pol-visibilities} \\
& Gridding ($t_\textrm{acc}$) & $\frac{8 n_\textrm{p}^4 (2^2 N_\textrm{ka}) N_\textrm{a/s} (N_\textrm{a/s}-1)/2}{(D_\textrm{s}/D_\textrm{a})^2}$ & $\frac{8 n_\textrm{p}^4 (2^2 N_\textrm{ks}) N_\textrm{s} (N_\textrm{s}-1)/2}{(D_\textrm{A}/D_\textrm{s})^2}$ & \ref{eqn:intra-station-opt-pol-corr-image}, \ref{eqn:inter-station-opt-pol-corr-image} \\
& FFT ($t_\textrm{acc}$) & $8 n_\textrm{p}^2 \frac{r}{\log_2 r} \log_2\left(\frac{D_\textrm{s}}{D_\textrm{a}}\right)^2$ & $8 n_\textrm{p}^2 \frac{r}{\log_2 r} \log_2\left(\frac{D_\textrm{A}}{D_\textrm{S}}\right)^2$ & \ref{eqn:intra-station-opt-pol-corr-image}, \ref{eqn:inter-station-opt-pol-corr-image} \\

@@

\subsection{LAMBDA-I}

\subsection{SKA-low}

\subsection{SKA-low Core}

\subsection{CASPA}

\subsection{FarView}

@@

\appendix

\section{Mathematical Details of Architectures}

\subsection{Co-polar Interferometry}\label{sec:copolar-interferometry}

If we represent $\mathcal{E}^\alpha(\hat{\boldsymbol{s}},\nu,t)$ as the spectral Fourier components, $\nu$, of the time-domain electric fields, $\mathcal{E}_{t^\prime}(\alpha,\hat{\boldsymbol{s}},t^\prime)$, emanating from astrophysical sources of emission in directions denoted by the unit vector, $\hat{\boldsymbol{s}}$ measured over a finite time interval, $T$, centered around time, $t$, then:
\begin{align}
    \mathcal{E}^\alpha(\hat{\boldsymbol{s}},\nu,t) = \frac{1}{T}\int\limits_{t-T/2}^{t+T/2} \mathcal{E}_{t^\prime}^\alpha(\hat{\boldsymbol{s}},t^\prime) e^{-i 2\pi \nu t^\prime} \mathrm{d}t^\prime,
\end{align}
where, superscript $\alpha\in\{1,2\}$ denotes the polarisation state of the radiation, $\nu$ denotes the spectral component or the frequency of radiation, $\lambda=c/\nu$ is the wavelength, where $c$ is the speed of light. Because all the operations considered in this paper operate independently on each spectral channel, $\nu$, and time, $t$, we will hereafter assume implicit dependence on $\nu$ and $t$ throughout without explicitly specifying it.

A measuring instrument, like an antenna in an aperture array, in the aperture plane will measure the superposition of these electric fields as they propagate from the sky locations spanning the celestial surface, $\mathbb{S}$, while imprinting its transfer function, $\mathcal{W}_{a_m}^{p\alpha}(\hat{\boldsymbol{s}})$, as
\begin{align}
    \underline{E}_{a_m}^p &= \int_\mathbb{S} \sum_\alpha  \mathcal{W}_{a_m}^{p\alpha}(\hat{\boldsymbol{s}})\, \mathcal{E}^\alpha(\hat{\boldsymbol{s}})\, e^{-i \frac{2\pi}{\lambda} \hat{\boldsymbol{s}}\cdot\boldsymbol{r}_{a_m}} \,\mathrm{d}\Omega \, , \label{eqn:polarimetric-Efield-element-ideal}
\end{align}

Electric fields in the aperture plane, $\underline{E}(\boldsymbol{r})$, can be written as a superposition of those that propagated from the astrophysical sources on the celestial surface $\mathbb{S}$, $\mathcal{E}(\hat{\boldsymbol{s}})$:
\begin{align}
    \underline{E}(\boldsymbol{r}) &= \int_\mathbb{S} \mathcal{E}(\hat{\boldsymbol{s}})\, e^{-i \frac{2\pi}{\lambda}\hat{\boldsymbol{s}}\cdot\boldsymbol{r}} \,\mathrm{d}\Omega,
\end{align}
where, the integral is over the celestial surface, $\mathbb{S}$, covered by the unit vector, $\hat{\boldsymbol{s}}$, $\boldsymbol{r}$ denotes the observer's location, $t$ denotes time, $\mathrm{d}\Omega=\mathrm{d}^2\hat{\boldsymbol{s}}$ is the infinitesimal solid angle element on the tangent plane of the celestial sphere perpendicular to the unit vector $\hat{\boldsymbol{s}}$.

Thus, the propagated electric field can be construed as a linear superposition of the electric fields emanating from astronomical sources with appropriate complex phases acquired during the propagation. Ignoring wide-field effects, this relation can be simplified as a Fourier transform of the electric fields in the sky coordinates.

% In the presence of a directional response of an ideal instrument, which includes but is not limited to the directional electric field pattern of the element, the electric field measured by the

In order to generalize later, we will consider a station indexed by $m$ as being made up of a group of $N_m$ elements, indexed by $a_m$. For now, we will focus on a single station, denoted by $m$.

The measuring instrument will imprint its transfer function on the measurements. If $\mathcal{W}_{a_m}(\hat{\boldsymbol{s}})$ is the directional electric field response of the element, $a_m$, then the electric field measured by this element will be ideally
\begin{align}
    \underline{E}_{a_m} &= \int_\mathbb{S} \mathcal{W}_{a_m}(\hat{\boldsymbol{s}})\, \mathcal{E}(\hat{\boldsymbol{s}})\, e^{-i \frac{2\pi}{\lambda} \hat{\boldsymbol{s}}\cdot\boldsymbol{r}_{a_m}} \,\mathrm{d}\Omega \, . \label{eqn:copolar-Efield-element-ideal}
\end{align}
In the typical case of non-ideal behavior of an element, the measured electric field will be potentially corrupted both in amplitude and phase relative to the ideal measurement in Equation~(\ref{eqn:copolar-Efield-element-ideal}). Then,
\begin{align}
    E_{a_m} &= g_{a_m}\underline{E}_{a_m} + n_{a_m} \, , \label{eqn:Efield-element}
\end{align}
where, $g_{a_m}$ denotes the multiplicative complex gain encapsulating the corruption of the wavefront due to instrumental and propagation effects, and $n_{a_m}$ denotes element-based additive noise in the measurement chain. A process of calibration is typically performed to remove the effects of this corruption by obtaining the best estimate, $\widehat{g}_{a_m}$, of the corrupting gain term, $g_{a_m}$, and the estimated electric field at the element after calibration will be:
\begin{align}
    \widehat{\underline{E}}_{a_m} &= \widehat{g}_{a_m}^{-1}\,E_{a_m} \, . \label{eqn:calibration}
\end{align}

% then $\mathcal{W}_{a_m}(\hat{\boldsymbol{s}})$ is the corresponding directional electric field response of the element. Thus, by application of Fourier transform properties, 
% \begin{align}
%     E_{a_m}^\textrm{I} &= \int_\mathbb{S} \mathcal{W}_{a_m}(\hat{\boldsymbol{s}})\, \mathcal{E}(\hat{\boldsymbol{s}})\, e^{-2\pi i\frac{\nu}{c} \boldsymbol{r}\cdot \hat{\boldsymbol{s}}} \,\mathrm{d}\Omega
% \end{align}

>>>>

A simultaneous beamforming filling the entire field of view can also be achieved by a two-dimensional spatial Fast Fourier Transform (FFT) of the measurements on the aperture plane. This can be enabled even for an irregular layout of station elements by gridding the calibrated electric fields measured by the station elements. The Optimal Map Making formalism \citep[OMM;][]{Tegmark1997a} formalism adopted by \citet{Morales2011} is the basis of the architecture called E-field Parallel Imaging Correlator \cite[EPIC;][]{Thyagarajan+2017},
\begin{align}
    \widetilde{\mathcal{E}}_m^\alpha(\hat{\boldsymbol{s}}_k) &= \sum_j \delta^2 \boldsymbol{r}_j \, e^{i\frac{2\pi}{\lambda} \hat{\boldsymbol{s}}_k\cdot\boldsymbol{r}_j} \left(\sum_{a_m} \sum_p \widetilde{W}_{a_m}^{p\alpha*}(\boldsymbol{r}_j-\boldsymbol{r}_{a_m}) \, \widetilde{E}_{a_m}^p \right) \, , \label{eqn:intra-station-pol-hol-img-epic}
\end{align}
whose equivalent linear algebraic representation is 
\begin{align}
    \widetilde{\boldsymbol{\mathcal{E}}}_{[m,\alpha,\hat{\boldsymbol{s}}]} &= \mathbf{F}^\textrm{H}_{[\hat{\boldsymbol{s}}\leftarrow \boldsymbol{r}]}\,\widetilde{\mathbf{W}}^\textrm{H}_{[\alpha,\boldsymbol{r}\leftarrow p,\boldsymbol{r}_{a_m}]}\,\widetilde{\mathbf{E}}_{[p,\boldsymbol{r}_{a_m}]} \, . \label{eqn:intra-station-pol-hol-img-epic-LA}
\end{align}

@@

@@

\begin{tabular}{cccccc}

@@

\headrow Architecture & Components & Intra-station & Inter-station & Timescale & Equations \\
 & & FLOP count & FLOP count & & \\ 
 & & (per station & (per voxel) & & \\
 & & per voxel) & & & \\

@@

VBF & Beamforming & $8 n_\textrm{p}^2 N_\textrm{a/s}$ & $8 n_\textrm{p}^2 N_\textrm{s}$ & $\delta t$ & \ref{eqn:intra-station-pol-hol-img-expl}, \ref{eqn:inter-station-pol-hol-img-expl} \\
& Squaring & $6 n_\textrm{p}^2$ & $6 n_\textrm{p}^2$ & $\delta t$ & \ref{eqn:intra-station-opt-pol-img-outprod} , \ref{eqn:inter-station-opt-pol-img-outprod}  \\
& Accumulation & $2 n_\textrm{p}^2$ & $2 n_\textrm{p}^2$ & $\delta t$ & \ref{eqn:intra-station-opt-pol-img-outprod}, \ref{eqn:inter-station-opt-pol-img-outprod} \\

@@

EPIC & Gridding & $\frac{6 n_\textrm{p}^2 N_\textrm{a/s} N_\textrm{ka}}{(D_\textrm{s}/D_\textrm{a})^2}$ & $\frac{6 n_\textrm{p}^2 N_\textrm{s} N_\textrm{ks}}{(D_\textrm{A}/D_\textrm{s})^2}$ & $\delta t$ & \ref{eqn:intra-station-pol-hol-img-epic-LA}, \ref{eqn:inter-station-pol-hol-img-epic-LA}   \\
& FFT & $8 n_\textrm{p} \frac{r}{\log_2 r} \gamma_\textrm{s}^2 \log_2\left(\gamma_\textrm{s}\frac{D_\textrm{s}}{D_\textrm{a}}\right)^2$ & $8 n_\textrm{p} \frac{r}{\log_2 r} \gamma_\textrm{A}^2 \log_2\left(\gamma_\textrm{A}\frac{D_\textrm{A}}{D_\textrm{S}}\right)^2$ & $\delta t$ & \ref{eqn:intra-station-pol-hol-img-epic-LA}, \ref{eqn:inter-station-pol-hol-img-epic-LA} \\
& Squaring & $6 n_\textrm{p}^2 \gamma_\textrm{s}^2$ & $6 n_\textrm{p}^2 \gamma_\textrm{A}^2$ & $\delta t$ & \ref{eqn:intra-station-opt-polarimetric-direct-img-LA}, \ref{eqn:inter-station-opt-polarimetric-direct-img-LA} \\
& Accumulation & $2 n_\textrm{p}^2 \gamma_\textrm{s}^2$ & $2 n_\textrm{p}^2 \gamma_\textrm{A}^2$ & $\delta t$ & \ref{eqn:intra-station-opt-polarimetric-direct-img-LA}, \ref{eqn:inter-station-opt-polarimetric-direct-img-LA} \\

@@

XBF & Correlator & $\frac{6 n_\textrm{p}^2 N_\textrm{a/s} (N_\textrm{a/s}-1)/2}{(D_\textrm{s}/D_\textrm{a})^2}$ & $\frac{6 n_\textrm{p}^2 N_\textrm{s} (N_\textrm{s}-1)/2}{(D_\textrm{A}/D_\textrm{s})^2}$ & $\delta t$ & \ref{eqn:intra-station-pol-visibilities}, \ref{eqn:inter-station-pol-visibilities}  \\
& Accumulation & $\frac{2 n_\textrm{p}^2 N_\textrm{a/s} (N_\textrm{a/s}-1)/2}{(D_\textrm{s}/D_\textrm{a})^2}$ & $\frac{2 n_\textrm{p}^2  N_\textrm{s} (N_\textrm{s}-1)/2}{(D_\textrm{A}/D_\textrm{s})^2}$ & $\delta t$ & \ref{eqn:intra-station-pol-visibilities}, \ref{eqn:inter-station-pol-visibilities}  \\
& DFT & $8 n_\textrm{p}^2 N_\textrm{a/s} (N_\textrm{a/s}-1)/2$ & $8 n_\textrm{p}^2 N_\textrm{s} (N_\textrm{s}-1)/2$ & $t_\textrm{acc}$ & \ref{eqn:intra-station-pol-xbf-img-expl}, \ref{eqn:inter-station-pol-xbf-img-expl}  \\

@@

XFFT & Correlator & $\frac{6 n_\textrm{p}^2 N_\textrm{a/s} (N_\textrm{a/s}-1)/2}{(D_\textrm{s}/D_\textrm{a})^2}$ & $\frac{6 n_\textrm{p}^2 N_\textrm{s} (N_\textrm{s}-1)/2}{(D_\textrm{A}/D_\textrm{s})^2}$ & $\delta t$ & \ref{eqn:intra-station-pol-visibilities}, \ref{eqn:inter-station-pol-visibilities}  \\
& Accumulation & $\frac{2 n_\textrm{p}^2 N_\textrm{a/s} (N_\textrm{a/s}-1)/2}{(D_\textrm{s}/D_\textrm{a})^2}$ & $\frac{2 n_\textrm{p}^2 N_\textrm{s} (N_\textrm{s}-1)/2}{(D_\textrm{A}/D_\textrm{s})^2}$ & $\delta t$ & \ref{eqn:intra-station-pol-visibilities}, \ref{eqn:inter-station-pol-visibilities} \\
& Gridding & $\frac{8 n_\textrm{p}^4 (2^2 N_\textrm{ka}) N_\textrm{a/s} (N_\textrm{a/s}-1)/2}{(D_\textrm{s}/D_\textrm{a})^2}$ & $\frac{8 n_\textrm{p}^4 (2^2 N_\textrm{ks}) N_\textrm{s} (N_\textrm{s}-1)/2}{(D_\textrm{A}/D_\textrm{s})^2}$ & $t_\textrm{acc}$ & \ref{eqn:intra-station-opt-pol-corr-image}, \ref{eqn:inter-station-opt-pol-corr-image} \\
& FFT & $8 n_\textrm{p}^2 \frac{r}{\log_2 r} \log_2\left(\frac{D_\textrm{s}}{D_\textrm{a}}\right)^2$ & $8 n_\textrm{p}^2 \frac{r}{\log_2 r} \log_2\left(\frac{D_\textrm{A}}{D_\textrm{S}}\right)^2$ & $t_\textrm{acc}$ & \ref{eqn:intra-station-opt-pol-corr-image}, \ref{eqn:inter-station-opt-pol-corr-image} \\

@@

\subsection{Station-scale Imaging Architectures}\label{sec:station-scale-imaging}

\subsection{Multi-scale Imaging Architectures}\label{sec:multi-scale-imaging}

Figure~\ref{fig:1D-coherent-compcost} shows a comparison of the compute cost densities in the discovery phase space of different multi-scale imaging architectures combining four options -- VBF, EPIC, XBF, and XFFT -- on the inter-station data with two options -- VBF and EPIC -- on the intra-station data for various array parameters and imaging cadences.

\begin{figure*}\ContinuedFloat
\subfloat[][\texttt{CASPA} \label{fig:1D-coherent-compcost-CASPA}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_CASPA.pdf}
} \\
\subfloat[][\texttt{FarView} \label{fig:1D-coherent-compcost-FarView}]
{\includegraphics[width=\textwidth]
{figures/1D_coherent_per_pixel_compcost_analysis_FarView.pdf}
}
\caption{Contd. Same as above but for (d) \texttt{CASPA}, and (e) \texttt{FarView} \label{fig:1D-coherent-compcost}}
\end{figure*}

In all cases, the intra-station full field of view data processing (first stage) is most efficiently achieved using EPIC (black lines) rather than VBF (gray lines). This is because of the relatively large number of elements densely packed in stations and due to the capability of simultaneous full field of view beamforming by the EPIC architecture powered by the FFT's efficiency.

The inter-station processing, however, varies significantly due to the diversity in the various inter-station array parameters and imaging cadence considered. For example, 
\begin{itemize}
    \item \texttt{LAMBDA-I} will benefit from deploying the correlator beamforming (XBF) architecture for inter-station processing. 
    \item \texttt{SKA1-low-core} will benefit from EPIC for the chosen parameters. However, if the number of stations, $N_\textrm{s}$, decreases,  the array diameter, $D_\textrm{A}$, increases or if the imaging cadence is slowed to $t_\textrm{acc} \gtrsim 5$~ms, the XFFT architecture starts to have an advantage over EPIC on the inter-station scale of data processing. 
    \item \texttt{SKA1-low} will benefit from the XFFT architecture for inter-station processing.
    \item \texttt{CASPA} will benefit from using the XBF architecture for inter-station processing due to significantly small number of stations.
    \item \texttt{FarView} appears to have an advantage in using XFFT for inter-station processing for the chosen parameters. If $N_\textrm{s}$ increases or if the cadence increases to $t_\textrm{acc}\lesssim 1$~ms, then EPIC becomes more efficient. 
\end{itemize}

\subsection{Effect of Imaging Cadence}\label{sec:cadence}

\begin{table*}[htb!]
\normalsize
\begin{threeparttable}
\caption{Impact of imaging cadence on choice of efficient imaging architecture.}
\label{tab:cadence}
% \begin{tabularx}{\textwidth}{ccccc}
\begin{tabular}{c|ccc|ccc}
\toprule
\headrow 
Array & & Intra-station & & & Inter-station & \\
 & $\lesssim 0.1$~ms & $\simeq 1$~ms & $\gtrsim 100$~ms & $\lesssim 0.1$~ms & $\simeq 1$~ms & $\gtrsim 100$~ms \\ 
\midrule\midrule

\texttt{LAMBDA-I} & EPIC & EPIC & EPIC & BF/XBF & XBF & XBF \\
\midrule
\texttt{SKA1-low-core} & EPIC & EPIC & EPIC & EPIC & EPIC & XFFT/EPIC/XBF \\
\midrule
\texttt{SKA1-low} & EPIC & EPIC & EPIC & XFFT/EPIC & XFFT & XFFT \\
\midrule
\texttt{CASPA} & EPIC & EPIC & XFFT & XBF & XBF & XBF \\
\midrule
\texttt{FarView} & EPIC & EPIC/XFFT & XFFT/XBF & EPIC & XFFT & XBF/XFFT \\
% \midrule
% Three & Four&three three\tnote{b} &four & & \\
\bottomrule
% \end{tabularx}
\end{tabular}
% \begin{tablenotes}[hang]
% % \item[]Table note
% \item[a]Array filling factor, $\,f_\textrm{A}=N_\textrm{s}\,(D_\textrm{s}/D_\textrm{A})^2$
% % \item[b]Station filling factor, $\,f_\textrm{s}=N_\textrm{a/s}\,(D_\textrm{a}/D_\textrm{s})^2$
% \end{tablenotes}
\end{threeparttable}
\end{table*}

% \subsection{LAMBDA-I}

% \subsection{SKA-low}

% \subsection{SKA-low Core}

% \subsection{CASPA}

% \subsection{FarView}

@@

% \appendix

% \section{Mathematical Details of Architectures}

% \subsection{Co-polar Interferometry}\label{sec:copolar-interferometry}

% If we represent $\mathcal{E}^\alpha(\hat{\boldsymbol{s}},\nu,t)$ as the spectral Fourier components, $\nu$, of the time-domain electric fields, $\mathcal{E}_{t^\prime}(\alpha,\hat{\boldsymbol{s}},t^\prime)$, emanating from astrophysical sources of emission in directions denoted by the unit vector, $\hat{\boldsymbol{s}}$ measured over a finite time interval, $T$, centered around time, $t$, then:
% \begin{align}
%     \mathcal{E}^\alpha(\hat{\boldsymbol{s}},\nu,t) = \frac{1}{T}\int\limits_{t-T/2}^{t+T/2} \mathcal{E}_{t^\prime}^\alpha(\hat{\boldsymbol{s}},t^\prime) e^{-i 2\pi \nu t^\prime} \mathrm{d}t^\prime,
% \end{align}
% where, superscript $\alpha\in\{1,2\}$ denotes the polarisation state of the radiation, $\nu$ denotes the spectral component or the frequency of radiation, $\lambda=c/\nu$ is the wavelength, where $c$ is the speed of light. Because all the operations considered in this paper operate independently on each spectral channel, $\nu$, and time, $t$, we will hereafter assume implicit dependence on $\nu$ and $t$ throughout without explicitly specifying it.

% A measuring instrument, like an antenna in an aperture array, in the aperture plane will measure the superposition of these electric fields as they propagate from the sky locations spanning the celestial surface, $\mathbb{S}$, while imprinting its transfer function, $\mathcal{W}_{a_m}^{p\alpha}(\hat{\boldsymbol{s}})$, as
% \begin{align}
%     \underline{E}_{a_m}^p &= \int_\mathbb{S} \sum_\alpha  \mathcal{W}_{a_m}^{p\alpha}(\hat{\boldsymbol{s}})\, \mathcal{E}^\alpha(\hat{\boldsymbol{s}})\, e^{-i \frac{2\pi}{\lambda} \hat{\boldsymbol{s}}\cdot\boldsymbol{r}_{a_m}} \,\mathrm{d}\Omega \, , \label{eqn:polarimetric-Efield-element-ideal}
% \end{align}

% Electric fields in the aperture plane, $\underline{E}(\boldsymbol{r})$, can be written as a superposition of those that propagated from the astrophysical sources on the celestial surface $\mathbb{S}$, $\mathcal{E}(\hat{\boldsymbol{s}})$:
% \begin{align}
%     \underline{E}(\boldsymbol{r}) &= \int_\mathbb{S} \mathcal{E}(\hat{\boldsymbol{s}})\, e^{-i \frac{2\pi}{\lambda}\hat{\boldsymbol{s}}\cdot\boldsymbol{r}} \,\mathrm{d}\Omega,
% \end{align}
% where, the integral is over the celestial surface, $\mathbb{S}$, covered by the unit vector, $\hat{\boldsymbol{s}}$, $\boldsymbol{r}$ denotes the observer's location, $t$ denotes time, $\mathrm{d}\Omega=\mathrm{d}^2\hat{\boldsymbol{s}}$ is the infinitesimal solid angle element on the tangent plane of the celestial sphere perpendicular to the unit vector $\hat{\boldsymbol{s}}$.

% Thus, the propagated electric field can be construed as a linear superposition of the electric fields emanating from astronomical sources with appropriate complex phases acquired during the propagation. Ignoring wide-field effects, this relation can be simplified as a Fourier transform of the electric fields in the sky coordinates.

% % In the presence of a directional response of an ideal instrument, which includes but is not limited to the directional electric field pattern of the element, the electric field measured by the

% In order to generalize later, we will consider a station indexed by $m$ as being made up of a group of $N_m$ elements, indexed by $a_m$. For now, we will focus on a single station, denoted by $m$.

% The measuring instrument will imprint its transfer function on the measurements. If $\mathcal{W}_{a_m}(\hat{\boldsymbol{s}})$ is the directional electric field response of the element, $a_m$, then the electric field measured by this element will be ideally
% \begin{align}
%     \underline{E}_{a_m} &= \int_\mathbb{S} \mathcal{W}_{a_m}(\hat{\boldsymbol{s}})\, \mathcal{E}(\hat{\boldsymbol{s}})\, e^{-i \frac{2\pi}{\lambda} \hat{\boldsymbol{s}}\cdot\boldsymbol{r}_{a_m}} \,\mathrm{d}\Omega \, . \label{eqn:copolar-Efield-element-ideal}
% \end{align}
% In the typical case of non-ideal behavior of an element, the measured electric field will be potentially corrupted both in amplitude and phase relative to the ideal measurement in Equation~(\ref{eqn:copolar-Efield-element-ideal}). Then,
% \begin{align}
%     E_{a_m} &= g_{a_m}\underline{E}_{a_m} + n_{a_m} \, , \label{eqn:Efield-element}
% \end{align}
% where, $g_{a_m}$ denotes the multiplicative complex gain encapsulating the corruption of the wavefront due to instrumental and propagation effects, and $n_{a_m}$ denotes element-based additive noise in the measurement chain. A process of calibration is typically performed to remove the effects of this corruption by obtaining the best estimate, $\widehat{g}_{a_m}$, of the corrupting gain term, $g_{a_m}$, and the estimated electric field at the element after calibration will be:
% \begin{align}
%     \widehat{\underline{E}}_{a_m} &= \widehat{g}_{a_m}^{-1}\,E_{a_m} \, . \label{eqn:calibration}
% \end{align}

% % then $\mathcal{W}_{a_m}(\hat{\boldsymbol{s}})$ is the corresponding directional electric field response of the element. Thus, by application of Fourier transform properties, 
% % \begin{align}
% %     E_{a_m}^\textrm{I} &= \int_\mathbb{S} \mathcal{W}_{a_m}(\hat{\boldsymbol{s}})\, \mathcal{E}(\hat{\boldsymbol{s}})\, e^{-2\pi i\frac{\nu}{c} \boldsymbol{r}\cdot \hat{\boldsymbol{s}}} \,\mathrm{d}\Omega
% % \end{align}

% % \begin{align}
% %     &= \int_\mathbb{R} W_{a_m}(\boldsymbol{r} - \boldsymbol{r}_{a_m}) \nonumber\\
% %     &\quad \times \left[\int_\textrm{S} \mathcal{E}(\hat{\boldsymbol{s}})\, e^{-2\pi i\nu \boldsymbol{r}\cdot \hat{\boldsymbol{s}}/c} \,\mathrm{d}\Omega\right]\, \mathrm{d}^2 \boldsymbol{r} + n_{a_m} \\
% %     &= \int_\textrm{S} \mathcal{W}_{a_m}(\hat{\boldsymbol{s}})\, \mathcal{E}(\hat{\boldsymbol{s}})\, e^{-2\pi i\nu \boldsymbol{r}\cdot \hat{\boldsymbol{s}}/c} \,\mathrm{d}\Omega \nonumber\\ 
% %     &\qquad + n_{a_m}  + n_{a_m}
% % \end{align}
% % The weighting, denoted by $W_{a_m}(\boldsymbol{r})$, encapsulates the aperture field illumination pattern of the element, the complex element gains (including direction-dependence) containing the effects of the propagation medium as well as of the instrumentation. $\mathcal{W}_{a_m}(\hat{\boldsymbol{s}})$ is the spatial Fourier transform of $W_{a_m}(\boldsymbol{r})$. If $W_{a_m}(\boldsymbol{r})$ denotes only the aperture field illumination pattern, then $\mathcal{W}_{a_m}(\hat{\boldsymbol{s}})$ is the corresponding directional element voltage response towards the celestial surface.
